ZCB Pricing

### 2018-08-04 ZCB Pricing .Rmd
Plots for sensitivity

senses <- matrix(nrow=13, ncol=9) # matrix to hold prices for various parameters
colnames(senses) <-c("Parameters","Closed Form","Crude Monte Carlo","Antithetic Variates","Moment Matching","Control Variates","Explicit","Implicit","Crank-Nicholson")

@@

#alpha=0.016
senses[9,2]=bond_price(alpha=0.016)
senses[9,3]=Crude_Monte_Carlo(alpha=0.016)
senses[9,4]=Antithetic_variates(alpha=0.016)
senses[9,5]=Moment_Matching(alpha=0.016)
senses[9,6]=Control_Variates_estimate(alpha=0.016)
senses[9,7]=explicit(alpha=0.016)
senses[9,8]=implicit(alpha=0.016)
senses[9,9]=CN(alpha=0.016)

@@

#beta=0.16
senses[11,2]=bond_price(beta=0.16)
senses[11,3]=Crude_Monte_Carlo(beta=0.16)
senses[11,4]=Antithetic_variates(beta=0.16)
senses[11,5]=Moment_Matching(beta=0.16)
senses[11,6]=Control_Variates_estimate(beta=0.16)
senses[11,7]=explicit(beta=0.16)
senses[11,8]=implicit(beta=0.16)
senses[11,9]=CN(beta=0.16)

@@

#alpha=0.016,beta=0.16
senses[13,2]=bond_price(alpha=0.016,beta=0.16)
senses[13,3]=Crude_Monte_Carlo(alpha=0.016,beta=0.16)
senses[13,4]=Antithetic_variates(alpha=0.016,beta=0.16)
senses[13,5]=Moment_Matching(alpha=0.016,beta=0.16)
senses[13,6]=Control_Variates_estimate(alpha=0.016,beta=0.16)
senses[13,7]=explicit(alpha=0.016,beta=0.16)
senses[13,8]=implicit(alpha=0.016,beta=0.16)
senses[13,9]=CN(alpha=0.016,beta=0.16)

par(mfrow = c(2,2))
first <- as.vector(senses[1,2:9])
plot(1:8,first, ylim =c(0.58,0.66))
test <- as.vector(senses[2, 2:9])
lines(1:8, test, col="red")
lines(1:8, senses[3,2:9],col ="blue")
```

>>>>

senses <- matrix(nrow=13, ncol=9) # matrix to hold prices for various parameters
colnames(senses) <-c("Parameters","Closed Form","Crude Monte Carlo","Antithetic Variates","Moment Matching","Control Variates","Explicit","Implicit","Crank-Nicholson")
xvec=c(Closed Form,Crude Monte Carlo,Antithetic Variates,Moment Matching,Control Variates,Explicit,Implicit,Crank Nicholson) #list of numerical methods

@@

#alpha=0.16
senses[9,2]=bond_price(alpha=0.16)
senses[9,3]=Crude_Monte_Carlo(alpha=0.16)
senses[9,4]=Antithetic_variates(alpha=0.16)
senses[9,5]=Moment_Matching(alpha=0.16)
senses[9,6]=Control_Variates_estimate(alpha=0.16)
senses[9,7]=explicit(alpha=0.16)
senses[9,8]=implicit(alpha=0.16)
senses[9,9]=CN(alpha=0.16)

@@

#beta=1.6
senses[11,2]=bond_price(beta=1.6)
senses[11,3]=Crude_Monte_Carlo(beta=1.6)
senses[11,4]=Antithetic_variates(beta=1.6)
senses[11,5]=Moment_Matching(beta=1.6)
senses[11,6]=Control_Variates_estimate(beta=1.6)
senses[11,7]=explicit(beta=1.6)
senses[11,8]=implicit(beta=1.6)
senses[11,9]=CN(beta=1.6)

@@

#alpha=0.16,beta=1.6
senses[13,2]=bond_price(alpha=0.16,beta=1.6)
senses[13,3]=Crude_Monte_Carlo(alpha=0.16,beta=1.6)
senses[13,4]=Antithetic_variates(alpha=0.16,beta=1.6)
senses[13,5]=Moment_Matching(alpha=0.16,beta=1.6)
senses[13,6]=Control_Variates_estimate(alpha=0.16,beta=1.6)
senses[13,7]=explicit(alpha=0.16,beta=1.6)
senses[13,8]=implicit(alpha=0.16,beta=1.6)
senses[13,9]=CN(alpha=0.16,beta=1.6)

plot(x=1:8,y=senses[1,2:9], ylim =c(0.58,0.66), xlab = "Numerical Method", ylab = "Bond Price", main = "Sensitivity Test: Interest Rate")
#axis(1, at=1:8, labels=xvec)
lines(1:8, senses[2,2:9], col="red",type = "p")
lines(1:8, senses[3,2:9],col ="blue",type = "p")
legend("bottomright", inset = c(-0,0), legend = c("r=0.05", "r=0.08", "r=0.1"), lty = c(1,1,1), col = c("red","black","blue", "red"), cex = 0.8, bty ="n")

plot(x=1:8,y=senses[1,2:9], ylim =c(0,2.2), xlab = "Numerical Method", ylab = "Bond Price", main = "Sensitivity Test: Time to maturity")
#axis(1, at=1:8, labels=xvec)
lines(1:8, senses[4,2:9], col="red",type = "p")
lines(1:8, senses[5,2:9],col ="blue",type = "p")
legend("topright", inset = c(-0,0), legend = c("T=1", "T=5", "T=10"), lty = c(1,1,1), col = c("red","black","blue", "red"), cex = 0.8, bty ="n")

plot(x=1:8,y=senses[1,2:9], ylim =c(0,2.2), xlab = "Numerical Method", ylab = "Bond Price", main = "Sensitivity Test: Variance")
#axis(1, at=1:8, labels=xvec)
lines(1:8, senses[6,2:9], col="red",type = "p")
lines(1:8, senses[7,2:9],col ="blue",type = "p")
legend("bottomright", inset = c(-0,0), legend = c("sigma=0.001", "sigma=0.005", "sigma=0.1"), lty = c(1,1,1), col = c("red","black","blue", "red"), cex = 0.8, bty ="n")

plot(x=1:8,y=senses[1,2:9], ylim =c(0,2.2), xlab = "Numerical Method", ylab = "Bond Price", main = "Sensitivity Test: Alpha")
#axis(1, at=1:8, labels=xvec)
lines(1:8, senses[8,2:9], col="red",type = "p")
lines(1:8, senses[9,2:9],col ="blue",type = "p")
legend("bottomright", inset = c(-0,0), legend = c("alpha=0.01", "alpha=0.08", "alpha=0.16"), lty = c(1,1,1), col = c("red","black","blue", "red"), cex = 0.8, bty ="n")

plot(x=1:8,y=senses[1,2:9], ylim =c(0,2.2), xlab = "Numerical Method", ylab = "Bond Price", main = "Sensitivity Test: Beta")
#axis(1, at=1:8, labels=xvec)
lines(1:8, senses[10,2:9], col="red",type = "p")
lines(1:8, senses[11,2:9],col ="blue",type = "p")
legend("topright", inset = c(-0,0), legend = c("beta=0.1", "beta=0.8", "beta=1.6"), lty = c(1,1,1), col = c("red","black","blue", "red"), cex = 0.8, bty ="n")

plot(x=1:8,y=senses[1,2:9], ylim =c(0,2.2), xlab = "Numerical Method", ylab = "Bond Price", main = "Sensitivity Test: Alpha & Beta")
#axis(1, at=1:8, labels=xvec)
lines(1:8, senses[12,2:9], col="red",type = "p")
lines(1:8, senses[13,2:9],col ="blue",type = "p")
legend("topright", inset = c(-0,0), legend = c("alpha=0.01,beta=0.1", "alpha=0.08,beta=0.8", "alpha=0.16,beta=1.6"), lty = c(1,1,1), col = c("red","black","blue", "red"), cex = 0.8, bty ="n")
```
